---
title: "R Notebook"
output: html_notebook
---


---
title: "Can Ale Bivariate"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
First, load all the necessary packages to run the script.

```{r}
library(tidyverse) # ggplot2, dplyr, tidyr, readr, purrr, tibble
library(magrittr) # pipes

library(sf) # spatial data handling
library(raster) # raster handling (needed for relief)
library(viridis) # viridis color scale
library(cowplot) 

library(tidyverse) 
library(cancensus)
```

Next, import the CanALE data file and assign it to an object to be able to work with it.
```{r}
library(sf)
CanALE_space <- st_read(
  "/Users/Robin/Dropbox/SUS MSSI/Bivariate Analysis/data/Mtl_DA_CANALE/Mtl_DA_CANALE.shp")
#plot(CanALE_space)

```

In this section, we create all the variables we want to compare in our bivariate analysis. 
We use the existing CanALE data to run calculations and create new combinations of variables in additional columns, which we will use later in the rest of the analysis. We do this using the mutate() function to create new columns. 

Variables:
ale_index
pct_active_transit (walk + bike to work)
pct_under40k
pct_over40k
pct_Imm (immigrant)
AvVal
AvRent


```{r}

## Make variables
names(CanALE_space)
# plot(CanALE_space[37])
# plot(CanALE_space[33])

CanALE_space <- CanALE_space %>% 
  rowwise() %>% 
  mutate(pct_Imm = Imm/Pop) %>% 
  mutate(pct_walked = Walked/Mode) %>% 
  mutate(pct_biked = Bicycle/Mode) %>% 
  mutate(pct_pubtrans = Pubtrans/Mode) %>% 
  mutate(pct_active_trans = sum(Bicycle, Walked)/Mode) %>% 
  mutate(pct_pubwalkbike = sum(Pubtrans, Bicycle, Walked)/Mode) %>% 
  mutate(pct_under40k = sum(Under_5k, IN5k_10k, IN10k_15k, IN15k, IN20k_25k, IN25k_30k, IN30k_35k, IN35k_40k)/Households) %>% 
   mutate(pct_over40k = sum(IN40k_45k, IN45k_50k, IN50k_60k, IN60k_70k, IN70k_80k, IN80k_90k,
                            IN90k, INOver100k)/Households) %>% 
  ungroup() %>% 
  st_as_sf
  
```

In this section, we assign a bivariate color scale to each pair of variables to analyze. 
Because of the structure of the code, each pair needs to be coded separately to its own color scale so that we will late be able to compare bivariate analyses. 

#Compute crossover input
```{r}
# create color scale that encodes two variables
# red for gini and blue for mean income
# the special notation with gather is due to readibility reasons
biv_color_ale_index_AvVal <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_ale_index_AvVal", "fill_ale_index_AvVal")

biv_color_ale_index_pct_under40k <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_ale_index_pct_under40k", "fill_ale_index_pct_under40k")

biv_color_ale_index_pct_over40k <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_ale_index_pct_over40k", "fill_ale_index_pct_over40k")

biv_color_ale_index_pct_Imm <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_ale_index_pct_Imm", "fill_ale_index_pct_Imm")

biv_color_ale_tranis_AvVal<- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_ale_tranis_AvVal", "fill_ale_tranis_AvVal")

biv_color_ale_tranis_pct_under40k <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_ale_tranis_pct_under40k", "fill_ale_tranis_pct_under40k")

biv_color_ale_tranis_pct_over40k <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_ale_tranis_pct_over40k", "fill_ale_tranis_pct_over40k")

biv_color_ale_tranis_pct_Imm <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_ale_tranis_pct_Imm", "fill_ale_tranis_pct_Imm")

biv_color_pct_Imm_pct_walked <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_pct_Imm_pct_Walked", "fill_pct_Imm_pct_Walked")

biv_color_pct_Imm_pct_active_trans <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_pct_Imm_pct_active_trans", "fill_pct_Imm_pct_active_trans")

biv_color_pct_Imm_pct_pubwalkbike <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_pct_Imm_pct_pubwalkbike", "fill_pct_Imm_pct_pubwalkbike")

biv_color_pct_Imm_AvRent <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_pct_Imm_AvRent", "fill_pct_Imm_AvRent")

biv_color_pct_Imm_pct_under40k <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_pct_Imm_pct_under40k", "fill_pct_Imm_pct_under40k")

biv_color_pct_Imm_pct_over40k <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_pct_Imm_pct_over40k", "fill_pct_Imm_pct_over40k")

biv_color_pct_active_trans_AvRent <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_pct_active_trans_AvRent", "fill_pct_active_trans_AvRent")

biv_color_pct_pubwalkbike_AvRent <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_pct_pubwalkbike_AvRent", "fill_pct_pubwalkbike_AvRent")

biv_color_pct_active_trans_AvVal <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_pct_active_trans_AvVal", "fill_pct_active_trans_AvVal")

biv_color_pct_pubwalkbike_AvVal <- tibble(
  "3 - 3" = "#3F2949", # high inequality, high income
  "2 - 3" = "#435786",
  "1 - 3" = "#4885C1", # low inequality, high income
  "3 - 2" = "#77324C",
  "2 - 2" = "#806A8A", # medium inequality, medium income
  "1 - 2" = "#89A1C8",
  "3 - 1" = "#AE3A4E", # high inequality, low income
  "2 - 1" = "#BC7C8F",
  "1 - 1" = "#CABED0" # low inequality, low income
) %>%
  gather("gr_pct_pubwalkbike_AvVal", "fill_pct_pubwalkbike_AvVal")


```

Here we extract quantiles from each variable. The quantiles are extracted by splitting the variable values into three classes. This distributes each variable into the same number of quantiles, which we will then be able to cross with a second variable to create our bivariate analysis.

```{r}
## variable quantiles

#bivariate <- cbind(ro, house_poor$percent_house_poor)

# define number of classes
no_classes <- 3

# extract quantiles
quantiles_ale_index <- CanALE_space %>% drop_na() %>%
  pull(ale_index) %>% 
  quantile(probs = seq(0, 1, length.out = no_classes + 1)) %>%
  as.vector() # to remove names of quantiles, so idx below is numeric

quantiles_pct_active_trans <- CanALE_space %>% drop_na() %>%
  pull(pct_active_trans) %>% 
  quantile(probs = seq(0, 1, length.out = no_classes + 1)) %>%
  as.vector() # to remove names of quantiles, so idx below is numeric

quantiles_pct_under40k <- CanALE_space %>% drop_na() %>%
  pull(pct_under40k) %>% 
  quantile(probs = seq(0, 1, length.out = no_classes + 1)) %>%
  as.vector() # to remove names of quantiles, so idx below is numeric

quantiles_pct_over40k <- CanALE_space %>% drop_na() %>%
  pull(pct_over40k) %>% 
  quantile(probs = seq(0, 1, length.out = no_classes + 1)) %>%
  as.vector() # to remove names of quantiles, so idx below is numeric

quantiles_pct_Imm <- CanALE_space %>% drop_na() %>%
  pull(pct_Imm) %>% 
  quantile(probs = seq(0, 1, length.out = no_classes + 1)) %>%
  as.vector() # to remove names of quantiles, so idx below is numeric

quantiles_ale_tranis <- CanALE_space %>% drop_na() %>%
  pull(ale_tranis) %>% 
  quantile(probs = seq(0, 1, length.out = no_classes + 1)) %>%
  as.vector() # to remove names of quantiles, so idx below is numeric

quantiles_AvVal <- CanALE_space %>% drop_na() %>%
  pull(AvVal) %>% 
  quantile(probs = seq(0, 1, length.out = no_classes + 1)) %>%
  as.vector() # to remove names of quantiles, so idx below is numeric

quantiles_AvRent <- CanALE_space %>% drop_na() %>%
  pull(AvRent) %>% 
  quantile(probs = seq(0, 1, length.out = no_classes + 1)) %>%
  as.vector() # to remove names of quantiles, so idx below is numeric

quantiles_pct_walked <- CanALE_space %>% drop_na() %>%
  pull(pct_walked) %>% 
  quantile(probs = seq(0, 1, length.out = no_classes + 1)) %>%
  as.vector() # to remove names of quantiles, so idx below is numeric

quantiles_pct_biked <- CanALE_space %>% drop_na() %>%
  pull(pct_biked) %>% 
  quantile(probs = seq(0, 1, length.out = no_classes + 1)) %>%
  as.vector() # to remove names of quantiles, so idx below is numeric

quantiles_pct_active_trans <- CanALE_space %>% drop_na() %>%
  pull(pct_active_trans) %>% 
  quantile(probs = seq(0, 1, length.out = no_classes + 1)) %>%
  as.vector() # to remove names of quantiles, so idx below is numeric

quantiles_pct_pubwalkbike <- CanALE_space %>% drop_na() %>%
  pull(pct_pubwalkbike) %>% 
  quantile(probs = seq(0, 1, length.out = no_classes + 1)) %>%
  as.vector() # to remove names of quantiles, so idx below is numeric

#quantiles_variable_2[2] <- 0.001 #cheat


```

In order to use the quantiles for the analysis, we must 

# Merge datasets, calculate quantiles, and add new field for match id for coloring

```{r}
## cbind variable quantile pairs

# Variable: ale_index , pct_under40k

cbind(quantiles_ale_index, quantiles_pct_under40k)

# # here we create custom labels
# labels <- imap_chr(quantiles, function(., idx){
#   return(paste0(round(quantiles[idx] , 2),
#                              "",
#                              " – ",
#                              round(quantiles[idx + 1] , 2),
#                              ""))
# })

labels <- c("1", "2", "3", "4")

# we need to remove the last label 
# because that would be something like "478k - NA"
labels <- labels[1:length(labels) - 1]

# here we actually create a new 
# variable on the dataset with the quantiles
bivariate_quantiles_ale_index_pct_under40k <- CanALE_space %>%
  mutate(mean_quantiles_ale_index = cut(ale_index,
                               breaks = quantiles_ale_index,
                               labels = labels,
                               include.lowest = T)) %>%
  mutate(mean_quantiles_pct_under40k = cut(pct_under40k,
                               breaks = quantiles_pct_under40k,
                               labels = labels,
                               include.lowest = T)) %>% 
  mutate(
    
    # by pasting the factors together as numbers we match the groups defined
    # in the tibble bivariate_color_scale
    gr_ale_index_pct_under40k = paste(
      as.numeric(mean_quantiles_ale_index), "-",
      as.numeric(mean_quantiles_pct_under40k)
    )
  ) %>%
  # we now join the actual hex values per "group"
  # so each municipality knows its hex value based on the his gini and avg
  # income value
  left_join(biv_color_ale_index_pct_under40k, by = "gr_ale_index_pct_under40k")
#bivariate_quantiles$fill

# Variables: ale_index , pct_over40k

cbind(quantiles_ale_index, quantiles_pct_over40k)
labels <- c("1", "2", "3", "4")
labels <- labels[1:length(labels) - 1]

bivariate_quantiles_ale_index_pct_over40k <- CanALE_space %>%
  mutate(mean_quantiles_ale_index = cut(ale_index,
                               breaks = quantiles_ale_index,  
                               labels = labels,
                               include.lowest = T)) %>%
  mutate(mean_quantiles_pct_over40k = cut(pct_over40k,
                               breaks = quantiles_pct_over40k,
                               labels = labels,
                               include.lowest = T)) %>% 
  mutate(
    gr_ale_index_pct_over40k = paste(
      as.numeric(mean_quantiles_ale_index), "-",
      as.numeric(mean_quantiles_pct_over40k)
    )
  ) %>%

  left_join(biv_color_ale_index_pct_over40k, by = "gr_ale_index_pct_over40k")

# Variables: ale_index , pct_Imm

cbind(quantiles_ale_index, quantiles_pct_Imm)
labels <- c("1", "2", "3", "4")
labels <- labels[1:length(labels) - 1]

bivariate_quantiles_ale_index_pct_Imm <- CanALE_space %>%
  mutate(mean_quantiles_ale_index = cut(ale_index,
                               breaks = quantiles_ale_index,
                               labels = labels,
                               include.lowest = T)) %>%
  mutate(mean_quantiles_pct_Imm = cut(pct_Imm,
                               breaks = quantiles_pct_Imm,
                               labels = labels,
                               include.lowest = T)) %>% 
  mutate(
    gr_ale_index_pct_Imm = paste(
      as.numeric(mean_quantiles_ale_index), "-",
      as.numeric(mean_quantiles_pct_Imm)
    )
  ) %>%

  left_join(biv_color_ale_index_pct_Imm, by = "gr_ale_index_pct_Imm")

# Variables: ale_tranis , AvVal

cbind(quantiles_ale_tranis, quantiles_AvVal)
labels <- c("1", "2", "3", "4")
labels <- labels[1:length(labels) - 1]

bivariate_quantiles_ale_tranis_AvVal <- CanALE_space %>%
  mutate(mean_quantiles_ale_tranis = cut(ale_tranis,
                               breaks = quantiles_ale_tranis,
                               labels = labels,
                               include.lowest = T)) %>%
  mutate(mean_quantiles_AvVal = cut(AvVal,
                               breaks = quantiles_AvVal,
                               labels = labels,
                               include.lowest = T)) %>% 
  mutate(
   gr_ale_tranis_AvVal = paste(
      as.numeric(mean_quantiles_ale_tranis), "-",
      as.numeric(mean_quantiles_AvVal)
    )
  ) %>%

  left_join(biv_color_ale_tr, by = "gr_ale_index_pct_over40k")


```


```{r}
## cbind variable quantile pairs



```



```{r}
## assign bivariate color scale fills to quantile variable pairs

## Variables: 1, 3
bivariate_color_scale_var1_var3 %<>%
  separate(gr_var1_var3, into = c("mean_quantiles_variable_one", "mean_quantiles_variable_three"), sep = " - ") %>%
  mutate(mean_quantiles_variable_one = as.integer(mean_quantiles_variable_one),
         mean_quantiles_variable_three = as.integer(mean_quantiles_variable_three)
         )

legend <- ggplot() +
  geom_tile(
    data = bivariate_color_scale_var1_var3,
    mapping = aes(
      x = mean_quantiles_variable_three,
      y = mean_quantiles_variable_one,
      fill = fill_var1_var3)
  ) +
  scale_fill_identity() +
  labs(x = "Higher income (up to 40k) ->",
       y = "More active living environment ->") +
  theme_map() +
  # make font small enough
  theme(
    axis.title = element_text(size = 6)
  ) +
  # quadratic tiles
  coord_fixed()

legend

## Variables: 1, 4

bivariate_color_scale_var1_var4 %<>%
  separate(gr_var1_var4, into = c("mean_quantiles_variable_one", "mean_quantiles_variable_four"), sep = " - ") %>%
  mutate(mean_quantiles_variable_one = as.integer(mean_quantiles_variable_one),
         mean_quantiles_variable_four = as.integer(mean_quantiles_variable_four)
         )

legend <- ggplot() +
  geom_tile(
    data = bivariate_color_scale_var1_var4,
    mapping = aes(
      x = mean_quantiles_variable_four,
      y = mean_quantiles_variable_one,
      fill = fill_var1_var4)
  ) +
  scale_fill_identity() +
  labs(x = "Higher income (above 40k) ->",
       y = "More active living environment ->") +
  theme_map() +
  # make font small enough
  theme(
    axis.title = element_text(size = 6)
  ) +
  # quadratic tiles
  coord_fixed()

legend
```


# Map theme settings
```{r}
default_background_color <- "transparent"
  default_font_color <- "black"
  default_font_family <- "Helvetica"
  
theme_map <- function(...) {
  default_background_color <- "transparent"
  default_font_color <- "black"
  default_font_family <- "Helvetica"
  
  theme_minimal() +
  theme(
    text = element_text(family = default_font_family,
                        color = default_font_color),
    # remove all axes
    axis.line = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    # add a subtle grid
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # background colors
    plot.background = element_rect(fill = default_background_color,
                                   color = NA),
    panel.background = element_rect(fill = default_background_color,
                                    color = NA),
    legend.background = element_rect(fill = default_background_color,
                                     color = NA),
    # borders and margins
    plot.margin = unit(c(.5, .5, .2, .5), "cm"),
    panel.border = element_blank(),
    panel.spacing = unit(c(-.1, 0.2, .2, 0.2), "cm"),
    # titles
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 22, hjust = 0,
                               color = default_font_color),
    plot.title = element_text(size = 15, hjust = 0.5,
                              color = default_font_color),
    plot.subtitle = element_text(size = 10, hjust = 0.5,
                                 color = default_font_color,
                                 margin = margin(b = -0.1,
                                                 t = -0.1,
                                                 l = 2,
                                                 unit = "cm"),
                                 debug = F),
    # captions
    plot.caption = element_text(size = 7,
                                hjust = .5,
                                margin = margin(t = 0.2,
                                                b = 0,
                                                unit = "cm"),
                                color = "#939184"),
    ...
  )
}
```



```{r}
#names(bivariate_quantiles)

## Variables: 1, 3

cropped_roads_var1_var3 <- st_intersection(bivariate_quantiles_var1_var3, st_buffer(st_centroid(st_union(bivariate_quantiles_var1_var3)), 26000))

cropped_roads_var1_var4 <- st_intersection(bivariate_quantiles_var1_var4, st_buffer(st_centroid(st_union(bivariate_quantiles_var1_var3)), 26000))
#bivariate_quantiles[which(is.na(bivariate_quantiles$fill.x)), 100] <- adjustcolor("white")
#bivariate_quantiles[which(is.na(bivariate_quantiles$fill.y)), 103] <- adjustcolor("white")

map_var_1 <-   ggplot(
  # use the same dataset as before
  data = cropped_roads_var1_var3
  ) +
  # first: draw the relief
  # geom_raster(
  #   data = relief,
  #   aes(
  #     x = x,
  #     y = y,
  #     alpha = value
  #   )
  # ) +
  # use the "alpha hack" (as the "fill" aesthetic is already taken)
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # color municipalities according to their gini / income combination
  geom_sf(
    aes(
      fill = mean_quantiles_variable_one
    ),
    # use thin white stroke for municipalities
    color = "white",
    size = 0
  ) +
  # as the sf object municipality_prod_geo has a column with name "fill" that
  # contains the literal color as hex code for each municipality, we can use
  # scale_fill_identity here
  scale_fill_identity() +
  # use the Viridis color scale
  scale_fill_viridis(
    option = "magma",
    name = "Active living index",
    alpha = 0.8, # make fill a bit brighter
    begin = 0.1, # this option seems to be new (compared to 2016):
    # with this we can truncate the
    # color scale, so that extreme colors (very dark and very bright) are not
    # used, which makes the map a bit more aesthetic
    end = 0.9,
    discrete = T, # discrete classes, thus guide_legend instead of _colorbar
    direction = 1, # dark is lowest, yellow is highest
    guide = guide_legend(
     keyheight = unit(5, units = "mm"),
     title.position = "top",
     reverse = T # display highest income on top
  )) +
  # use thicker white stroke for cantons
  # geom_sf(
  #   data = canton_geo,
  #   fill = "transparent",
  #   color = "white",
  #   size = 0.5
  # ) +
  # # draw lakes in light blue
  # geom_sf(
  #   data = lake_geo,
  #   fill = "#D6F1FF",
  #   color = "transparent"
  # ) +
  # add titles
  labs(x = NULL,
         y = NULL#,
         #subtitle = "Montreal's active living",
         #title = paste0("Percent of people spending more than 30% of income",
         #                  " on housing vs. ratio of renting tenants, 2016"),
         #caption = "Fig. 1. Active living index vs. average property value"
       ) +
  # add the theme
  theme_map() 

map_var_3 <-   ggplot(
  # use the same dataset as before
  data = cropped_roads_var1_var3
  ) +
  # first: draw the relief
  # geom_raster(
  #   data = relief,
  #   aes(
  #     x = x,
  #     y = y,
  #     alpha = value
  #   )
  # ) +
  # use the "alpha hack" (as the "fill" aesthetic is already taken)
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # color municipalities according to their gini / income combination
  geom_sf(
    aes(
      fill = mean_quantiles_variable_three
    ),
    # use thin white stroke for municipalities
    color = "white",
    size = 0.1
  ) +
  # as the sf object municipality_prod_geo has a column with name "fill" that
  # contains the literal color as hex code for each municipality, we can use
  # scale_fill_identity here
  scale_fill_identity() +
  # use the Viridis color scale
  scale_fill_viridis(
    option = "magma",
    name = "Average dwelling value",
    alpha = 0.8, # make fill a bit brighter
    begin = 0.1, # this option seems to be new (compared to 2016):
    end = 0.9,
    discrete = T, # discrete classes, thus guide_legend instead of _colorbar
    direction = 1, # dark is lowest, yellow is highest
    guide = guide_legend(
     keyheight = unit(5, units = "mm"),
     title.position = "top",
     reverse = T # display highest income on top
  )) +
  # use thicker white stroke for cantons
  # geom_sf(
  #   data = canton_geo,
  #   fill = "transparent",
  #   color = "white",
  #   size = 0.5
  # ) +
  # # draw lakes in light blue
  # geom_sf(
  #   data = lake_geo,
  #   fill = "#D6F1FF",
  #   color = "transparent"
  # ) +
  # add titles
  labs(x = NULL,
         y = NULL#,
         #subtitle = "Montreal's active living",
         #title = paste0("Percent of people spending more than 30% of income",
         #                  " on housing vs. ratio of renting tenants, 2016"),
         #caption = "Fig. 1. Active living index vs. average property value"
       ) +
  # add the theme
  theme_map()  

map_var_4 <-   ggplot(
  # use the same dataset as before
  data = cropped_roads_var1_var4
  ) +
  # first: draw the relief
  # geom_raster(
  #   data = relief,
  #   aes(
  #     x = x,
  #     y = y,
  #     alpha = value
  #   )
  # ) +
  # use the "alpha hack" (as the "fill" aesthetic is already taken)
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # color municipalities according to their gini / income combination
  geom_sf(
    aes(
      fill = mean_quantiles_variable_four
    ),
    # use thin white stroke for municipalities
    color = "white",
    size = 0.1
  ) +
  # as the sf object municipality_prod_geo has a column with name "fill" that
  # contains the literal color as hex code for each municipality, we can use
  # scale_fill_identity here
  scale_fill_identity() +
  # use the Viridis color scale
  scale_fill_viridis(
    option = "magma",
    name = "Average dwelling value",
    alpha = 0.8, # make fill a bit brighter
    begin = 0.1, # this option seems to be new (compared to 2016):
    end = 0.9,
    discrete = T, # discrete classes, thus guide_legend instead of _colorbar
    direction = 1, # dark is lowest, yellow is highest
    guide = guide_legend(
     keyheight = unit(5, units = "mm"),
     title.position = "top",
     reverse = T # display highest income on top
  )) +
  # use thicker white stroke for cantons
  # geom_sf(
  #   data = canton_geo,
  #   fill = "transparent",
  #   color = "white",
  #   size = 0.5
  # ) +
  # # draw lakes in light blue
  # geom_sf(
  #   data = lake_geo,
  #   fill = "#D6F1FF",
  #   color = "transparent"
  # ) +
  # add titles
  labs(x = NULL,
         y = NULL#,
         #subtitle = "Montreal's active living",
         #title = paste0("Percent of people spending more than 30% of income",
         #                  " on housing vs. ratio of renting tenants, 2016"),
         #caption = "Fig. 1. Active living index vs. average property value"
       ) +
  # add the theme
  theme_map()  

map_total_var1_var3 <-   ggplot(
  # use the same dataset as before
  data = cropped_roads_var1_var3
  ) +
  # first: draw the relief
  # geom_raster(
  #   data = relief,
  #   aes(
  #     x = x,
  #     y = y,
  #     alpha = value
  #   )
  # ) +
  # use the "alpha hack" (as the "fill" aesthetic is already taken)
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # color municipalities according to their gini / income combination
  geom_sf(
    aes(
      fill = fill_var1_var3
    ),
    # use thin white stroke for municipalities
    color = "white",
    size = 0
  ) +
  # as the sf object municipality_prod_geo has a column with name "fill" that
  # contains the literal color as hex code for each municipality, we can use
  # scale_fill_identity here
  scale_fill_identity() +
  # use thicker white stroke for cantons
  # geom_sf(
  #   data = canton_geo,
  #   fill = "transparent",
  #   color = "white",
  #   size = 0.5
  # ) +
  # # draw lakes in light blue
  # geom_sf(
  #   data = lake_geo,
  #   fill = "#D6F1FF",
  #   color = "transparent"
  # ) +
  # add titles
  labs(x = NULL,
         y = NULL,
         subtitle = "Montreal's immigration and active living index",
         title = paste0("Active Living Environments vs.",
                           "Median Household Income (< $40,000), 2016"),
         caption = "Fig. 1. Percentage of immigrants vs. active living index"
       ) +
  # add the theme
  theme_map() 

map_total_var1_var4 <-   ggplot(
  # use the same dataset as before
  data = cropped_roads_var1_var4
  ) +
  # first: draw the relief
  # geom_raster(
  #   data = relief,
  #   aes(
  #     x = x,
  #     y = y,
  #     alpha = value
  #   )
  # ) +
  # use the "alpha hack" (as the "fill" aesthetic is already taken)
  scale_alpha(name = "",
              range = c(0.6, 0),
              guide = F) + # suppress legend
  # color municipalities according to their gini / income combination
  geom_sf(
    aes(
      fill = fill_var1_var4
    ),
    # use thin white stroke for municipalities
    color = "white",
    size = 0
  ) +
  # as the sf object municipality_prod_geo has a column with name "fill" that
  # contains the literal color as hex code for each municipality, we can use
  # scale_fill_identity here
  scale_fill_identity() +
  # use thicker white stroke for cantons
  # geom_sf(
  #   data = canton_geo,
  #   fill = "transparent",
  #   color = "white",
  #   size = 0.5
  # ) +
  # # draw lakes in light blue
  # geom_sf(
  #   data = lake_geo,
  #   fill = "#D6F1FF",
  #   color = "transparent"
  # ) +
  # add titles
  labs(x = NULL,
         y = NULL,
         subtitle = "Montreal's immigration and active living index",
         title = paste0("Active Living Environments vs.",
                           "Median Household Income (> $40,000), 2016"),
         caption = "Fig. 1. Percentage of immigrants vs. active living index"
       ) +
  # add the theme
  theme_map() 

map_var_1
map_var_3
map_var_4
map_total_var1_var3
map_total_var1_var4


```


```{r}
ggdraw() +
  draw_plot(map_total_var1_var4, 0, 0, 1.05, 1.05) +
  draw_plot(legend, 0.015, 0.0, 0.35, 0.35) 
```